Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-02-13 ITiCSE2019.tex
Added Votipkaetal2019a and use of it.
Text for Ruiz2019a

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some Cybersecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
There are various levels of specialism at which Cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general CS graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]How might accreditation regard Cybersecurity Education, or help with it?
\end{description}
\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other Knowledge Areas.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, writes as follows
\begin{quote}
Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.
\end{quote}
\section{Policy Context}

@@

\subsection{Android}\label{sec:Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.

\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
The ESG survey is international, but ESG have confirmed that the UK figures are very similar.
%JHD possibly to write about his recruitment experiences.  ? more IoC input?

>>>>

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some Cybersecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
There are various levels of specialism at which Cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general CS graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]How might accreditation regard Cybersecurity Education, or help with it?
\end{description}
\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other Knowledge Areas.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, writes as follows
\begin{quote}
Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.
\end{quote}

But \cite[Table 1]{Ruiz2019a} shows that the UK situation is distinctly different: he quotes that 61\% of UK courses offer mandatory cybersecurity content, and his research was based on web scraping, it represents a lower bound.
\section{Policy Context}

@@

\subsection{Android}\label{sec:Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.
\par
The uncritical reading of Stack Overflow was also noted in \cite[Slide 29]{Votipkaetal2019a}. Their key recommendation  \cite[Slide 32]{Votipkaetal2019a} is ``Improve documentation: Clarify what you can(not) copy/paste''. 
\subsection{Staff}
It is well known that Cybersecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
The ESG survey is international, but ESG have confirmed that the UK figures are very similar.
%JHD possibly to write about his recruitment experiences.  ? more IoC input?
